\textbf{Response Letter}

### 2018-12-03 doc/aij18/major-revision/aij18.tex
First round of revision

\begin{abstract}
  This paper presents \FAMA, a novel approach for learning \strips\ action models from observations of plan executions that compiles the learning task into a classical planning task. Unlike all existing learning systems, \FAMA is able to learn when the actions of the plan executions are partially or totally unobservable and information on intermediate states is partially provided. This flexibility makes \FAMA an ideal learning approach in domains where only sensor data are accessible. Additionally, we leverage the compilation scheme and extend it to come up with an evaluation method that allows us to assess the quality of a learned model syntactically, that is, with respect to the actual model; and, semantically, that is, with respect to a set of observations of plan executions. We also show that the extended compilation scheme can be used to lay the foundations of a framework for action model comparison. \FAMA is exhaustively evaluated over a wide range of IPC domains and its performance is compared to \ARMS, a state-of-the-art benchmark in action model learning.
\end{abstract}

@@

Besides its capacity of working with minimal observability, \FAMA is also able to learn from very small amounts of input knowledge, a clear advantage in domains where obtaining enough training samples is difficult or costly. While the experimental evaluation shows in general an exponential increase of the computation time as the number of training traces augments, \FAMA is able to learn action models more accurate than those of \ARMS with very limited input knowledge. Unlike extensive-data ML approaches, our work explores an alternative research direction that exploits logic reasoning to learn sound models from minimal input knowledge.

>>>>

\begin{abstract}
  This paper presents \FAMA, a novel approach for learning \strips\ action models from observations of plan executions that compiles the learning task into a classical planning task. Unlike all existing learning systems, \FAMA is able to learn when the actions of the plan executions are partially or totally unobservable and information on intermediate states is partially provided. This flexibility makes \FAMA an ideal learning approach in domains where only sensoring data are accessible. Additionally, we leverage the compilation scheme and extend it to come up with an evaluation method that allows us to assess the quality of a learned model syntactically, that is, with respect to the actual model; and, semantically, that is, with respect to a set of observations of plan executions. We also show that the extended compilation scheme can be used to lay the foundations of a framework for action model comparison. \FAMA is exhaustively evaluated over a wide range of IPC domains and its performance is compared to \ARMS, a state-of-the-art benchmark in action model learning.
\end{abstract}

@@

Besides its capacity of working with minimal observability, \FAMA is also able to learn from very small amounts of input knowledge, a clear advantage in domains where obtaining enough training samples is difficult or costly. While the experimental evaluation shows in general an exponential increase of the computation time as the number of training traces augments, \FAMA is able to learn action models more accurate than those of \ARMS with very limited input knowledge. Unlike extensive-data ML approaches, our work explores an alternative research direction that exploits logic reasoning to learn sound models from minimal input observability.

### 2018-12-03 doc/aij18/major-revision/letter.tex
First round of revision

\begin{enumerate}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide at the end of the section the overall picture of our approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of the \FAMA approach that explains our pursued objective.

@@

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
I suggest to describe the overall concept of the learning approach first (see above for my hopefully correct summary) and to give the technical details later, rather than describing the technical details of compilation only without providing the overall picture. Going top down would make reading much easier. The second reason for revision is the comparison to ARMS.
\end{mdframed}

\textcolor{blue}{We agree with the reviewer that we should provide ....}

\begin{mdframed} [hidealllines=true,backgroundcolor=gray!20]
I suggest to compare with LOUGA that is better than ARMS in all aspects (runtime and quality of obtained models) so ARMS is no more state-of-the-art.
\end{mdframed}

\textcolor{blue}{As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that this system is built as a graphical interface application, which makes it impossible to automate the model learning process and evaluation process via a script for the 154 cases tested. Nevertheless, we did manually test a few cases for the \emph{blocksworld}, \emph{floor-tile}, \emph{n-puzzle} and \emph{transport} domains. The results showed similar performance among the two approaches, with each one performing better in two of the four domains tested.}

@@

  There are several cases where authors repeat themselves several times. Here are a few examples:
- (page 2) "While current learning systems …. none of them allow partial observability in the sequence of executed actions "

Two paragraphs later:

" ... unlike most relevant action-model learning algorithms, FAMA does not require the traces to contain any observed action ..."

(Page 8) "FAMA represents one step ahead ... without assuming observed actions."

@@

@@

\textcolor{blue}{We have rephrased (and highlighted in red) all the paragraphs and sentences pointed by the reviewer. With respect to the first comment, we attempt to make it clear that classical planning techniques can be used to generate a large variety of planning models, not only \strips\ models, and that these techniques underpin some relevant concepts that are also reusable in learning models when the behaviour of the agent is not available.}
\textcolor{blue}{With respect to the other two comments, besides using different expressions to refer to the two concepts, we have included some additional side explanations that we hope help understand the meaning of the sentences.}
\vspace{0.1cm}

@@

NO ESTA HECHO TODAVIA

>>>>

\begin{enumerate}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide an outline of the overall picture of our \FAMA approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of the \FAMA that explains our pursued objective.

@@

\vspace{0.3cm}

\textcolor{red}{Additionally, all the changes are highlighted in red in the document file.}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
I suggest to describe the overall concept of the learning approach first (see above for my hopefully correct summary) and to give the technical details later, rather than describing the technical details of compilation only without providing the overall picture. Going top down would make reading much easier.
\end{mdframed}

\textcolor{blue}{We agree with the reviewer that the paper lacks a description of the overall approach. We refer the reviewer to the main modification \#1 exposed above. Following the notes of the reviewer's summary, we have also included a brief summary at the end of the section Introduction that serves to wrap up the main features of \FAMA.}

\begin{mdframed} [hidealllines=true,backgroundcolor=gray!20]
The second reason for revision is the comparison to ARMS. I suggest to compare with LOUGA that is better than ARMS in all aspects (runtime and quality of obtained models) so ARMS is no more state-of-the-art.
\end{mdframed}

\textcolor{blue}{As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that this system is built as a graphical interface application, which makes it impossible to automate the model learning process and evaluation process via a script for the 154 cases tested. Nevertheless, we did manually test a few cases of the \emph{blocksworld}, \emph{floor-tile}, \emph{n-puzzle} and \emph{transport} domains. The results showed a similar performance of \FAMA and LOUGA, each performing better in two of the four tested domains.}

\textcolor[rgb]{1.00,0.00,0.00}{COMENTAR EL MIERCOLES}

@@

  There are several cases where authors repeat themselves several times. Here are a few examples:

- (page 2) "While current learning systems ... none of them allow partial observability in the sequence of executed actions "
Two paragraphs later: " ... unlike most relevant action-model learning algorithms, FAMA does not require the traces to contain any observed action ..."
(Page 8) "FAMA represents one step ahead ... without assuming observed actions."

@@

\textcolor{blue}{We have removed repetitions as much as possible. In the first example pointed by the reviewer, the explanation about partial observability of \FAMA and the other learning systems is concentrated in a single paragraph and the repetition is eliminated. Nevertheless, we think that at some points it is necessary to recall a particular concept in order to enhance the exposition of a further concept.}

\textcolor{blue}{With respect to the repetition of the definition of a \strips\ action model .... }

@@

\textcolor{blue}{We have rephrased all the paragraphs and sentences pointed by the reviewer. With respect to the first comment, we attempt to make it clear that classical planning techniques can be used to generate a large variety of planning models, not only \strips\ models, and that these techniques underpin some relevant concepts that are also reusable in learning models when the behaviour of the agent is not available.}
\textcolor{blue}{With respect to the other two comments, besides using different expressions to refer to the two concepts, we have included some additional side explanations that we hope help understand the meaning of the sentences.}
\vspace{0.1cm}

@@

\textcolor[rgb]{1.00,0.00,0.00}{NO ESTA HECHO TODAVIA}
